The Werewolf Among Us: Humans vs LLMs in Multi-Agent Games

### 2025-05-06 _tex/paper.tex
Built site for gh-pages

\title{The Werewolf Among Us: Humans vs LLMs in Multi-Agent Games}
\author{Bhavana Jonnalagadda \and Riley Jones}
\date{2025-05-01}
\begin{document}
\maketitle
\begin{abstract}
Abstract TODO
\end{abstract}

@@

\begin{itemize}
\tightlist
\item
  A description of the problem and its significance
\item
  How do LLMs function in a multi-agent environment?

  \begin{itemize}
  \tightlist
  \item
    Each has limited information
  \item
    Approximately the same ability, traits, skills
  \end{itemize}
\item
  We use LLMs to simulate whether synthetic agents can participate in
  complex, adversarial group dynamics
\item
  Werewolf is a good candiate for testing multi agent systems of
  cooperation and secrecy

  \begin{itemize}
  \tightlist
  \item
    Need citation
  \item
    The game tests adaptive reasoning, strategic alignment, and
    collective threat detection under special conditions
  \end{itemize}
\end{itemize}

@@

>>>>

\title{The Werewolf Among Us: Humans vs LLMs in Multi-Agent Games}
\author{Bhavana Jonnalagadda \and Riley Jones}
\date{2025-05-06}
\begin{document}
\maketitle
\begin{abstract}
Abstract TODO
\end{abstract}

@@

\begin{itemize}
\item
  Social deduction games like \emph{Werewolf} offer a clear way to
  evaluate how agents deceive, persuade, and reason in group
  settings(\citeproc{ref-wikiwerewolf}{Wikipedia contributors 2024}). In
  these games, players have limited information, hidden identities, and
  must convince others while trying to figure out who is lying. These
  challenges closely match real life situations involving trust,
  negotiation, and manipulation.
\item
  We wanted to compare how humans and large language models (LLMs)
  handle these situations. To do this, we used two recent datasets:

  \begin{itemize}
  \tightlist
  \item
    \emph{Werewolf Among Us} (Lai et al., 2022), a collection of real
    human gameplay annotated with persuasion strategies,
  \item
    \emph{Werewolf Arena} (Bailis et al., 2024), a simulated environment
    where LLM agents play the game autonomously.
  \item
    While both studies show Werewolf generates complex strategic
    language, neither compares human and LLM behavior directly.
  \end{itemize}
\item
  Our project addresses this gap. We analyzed transcripts from both
  datasets, matched them by role, round, and persuasion strategy, and
  compared how humans and LLMs lie, persuade, and detect deception.
\item
  By annotating utterances with the same set of persuasive strategies,
  we clearly show how synthetic agents differ from or resemble humans
  when navigating deception in adversarial group interactions.
\end{itemize}

@@

\bibitem[\citeproctext]{ref-wikiwerewolf}
Wikipedia contributors. 2024. {``Mafia (Party Game).''}
\url{https://en.wikipedia.org/wiki/Mafia_(party_game)}.
